\documentclass[12pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[colorlinks=true,linkcolor=blue]{hyperref}
\usepackage{graphicx,tikz}
\usepackage{float}
\usetikzlibrary{positioning}
\input defs.tex
\bibliographystyle{ieeetr}
\graphicspath{ {./figures/} }

\title{Progress Report}
\author{Peter Hartig}

\begin{document}
\subsection{Questions}
\begin{itemize}
\item 
For the channel model given by 
	\begin{equation}
	\mathbf{H}_{Total} =  \underbrace{\mathbf{C}_{2}\mathbf{H}_{2}\mathbf{P}_{2}\boldsymbol{\Phi}\mathbf{C}_{1}\mathbf{H}_{1}\mathbf{P}_{1}}_{\text{IRS}} + \underbrace{\mathbf{D}}_{\text{LOS} }
	\end{equation}
should the power added by the correlation matrix be normalized such that rows of matrix $\mathbf{C}_{i}$ have norm 1?
This ensure that the elements would still have the same variance despite being correlated. 
\item 
I notice that for the correlated channels (normalized) that if I perform water-filling the power allocation, the capacity is greater than for 
the iid channel. Is this correct? This result seems strange. 

\item 
In order to test the method discussed during our last meeting, I am using the following method to find the AED of the channel given by 
	\begin{equation}
	\mathbf{H}_{Total} = \mathbf{C}\mathbf{H}
	\end{equation}
	with C as a normalized correlation matrix with "blocks of correlation" and H is an iid gaussian matrix. 
	The fsolve function in matlab does not converge unless I use a closed form of the s-transform in which case the expected aed is found. This may be a result of having a distribution with delta masses*. If $\mathbf{C}$ is substituted with another gaussian iid matrix $\mathbf{H}_2 $, and I use the quarter circle stieltjes this method also does not work. This makes me think that something is wrong with equation \eqref{S_Stieltjes} below.
\begin{enumerate}
\item 
	\begin{equation}
	p(x) = \frac{1}{\pi} \underset{y \rightarrow \infty}{lim} \; Img(G(x+jy))
	\end{equation}
	
\item 
	\begin{equation}
	G(s)=  \frac{1}{s} (1+\gamma\left(\frac{1}{s}\right))
	\end{equation}
		
\item 
	\begin{equation}
	\gamma(z) =  \frac{z(1+\gamma(z))}{S(\gamma(z))}
	\end{equation}
\item 
	\begin{equation}
	S(z) = S_{\text{correlation}}(z) S_{\text{rayleigh}}(z)
	\end{equation}
	
	\item 
	\begin{equation}\label{S_Stieltjes}
	S_{\text{correlation}}(z)  = \frac{z+1}{z} \gamma^{-1}(z)
	\end{equation}

\item 
	\begin{equation}
	\gamma^{-1}(z) = \frac{-G(\frac{1}{\gamma^{-1}(z))}}{z+1})
	\end{equation}
	In this case I am using the known AED of the correlation matrix to find $G_{\text{correlation}}(s)$ using
	\begin{equation}
	G(s) = \int \frac{1}{x-s} dPx
	\end{equation}
	
\end{enumerate}
\end{itemize}

\end{document}
